Automated topic naming to support analysis of software maintenance activities

### 2010-08-19 icse/icse2011.tex
Unsupervised labelling edit part I

% word list similarity
Using our three word lists, we labeled our topics where there was a match between a word in the list and the same word in the topic.
Table \ref{tbl:wordlist} lists broad labeling results for MaxDB as an example. A \emph{named topic} is a topic with a matching label. There are \{periods X 20\} topics per project as we told LDA to extract 20 topics per period. All experiments were run on MaxDB 7.500 and MySQL 3.23 data.

@@

For \textsf{exp1}, our best performing labels (the labels matched with the most topics) were \emph{correctness} (182 topics) and \emph{testability} (121). We did not get good results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. We also looked for correlation between our labels: Excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability} and \emph{traceability}, and \emph{testability} and \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. As we mentioned, the word-lists are quite broad, so there are likely to be false-positives (discussed below). We found a high of 265 topics for \emph{usability}, with a low of 44 topics for \emph{maintainability}. Common co-occurrences were \emph{reliability} and \emph{usability}, \emph{efficiency} and \emph{reliability}, and \emph{efficiency} and \emph{usability} (200, 190, and 150 topics in common, respectively).

>>>>

% word list similarity
Using our three word lists, we labeled our topics where there was a match between a word in the list and the same word in the topic.
A \emph{named topic} is a topic with a matching label. 
There are roughly 20 times the number of topics as there are periods per project. 
This is because we told LDA to extract 20 topics per period. 
All experiments were run on MaxDB 7.500 and MySQL 3.23 data.
Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB
and MySQL.

@@

For \textsf{exp1}, our best performing labels, those with the most topics, were \emph{correctness} (182 topics) and \emph{testability} (121). 
We did not get good results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. 
We also looked for correlation between our labels: Excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability} with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are quite broad, so there are likely to be false-positives (discussed below). 
We found a high of 265 topics for \emph{usability}, with a low of 44 topics for \emph{maintainability}. 
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability} (200, 190, and 150 topics in common, respectively).
